---
title: "Speaking Many Languages: Finding Power and Joy in R and Python"
subtitle: "Speaker: Federica Gazzelloni" 
date: "2025-06-16"
author: <span style="color:#ff66c4;">R-Ladies Rome</span>
footer: "[Visit our Website: rladiesrome.org](http://www.rladiesrome.org)"
logo: images/logo.png 
logo-alt: "rladiesrome"
format: 
  revealjs:
    theme: [blood, custom.scss]
    scrollable: true
    transition: slide
    background-transition: fade
    incremental: true
    slide-number: true
editor: visual
---

# Welcome<br>Everyone! {background-image="images/logo.png" background-size="400px" background-position="right"}

# Disclaimer {.smaller}

This talk is recorded and will be posted on [Youtube \@rladiesrome](https://www.youtube.com/@rladiesrome)

Please remember that all our attendees are expected to adhere to our `Code of Conduct` 👉 <https://rladies.org/coc/>

<br>

**`We ensure a safe, inclusive, and harassment-free space for learning. We are committed to providing a respectful environment where everyone feels welcome to learn, connect, and grow.`**

# Who we are?

```         
rladies_global |>
  filter(city %in% c('Rome'))
```

**`R-Ladies Rome` is a local chapter of `R-Ladies Global` dedicated to promoting `continuous learning` in the Open Source Community. Our monthly meetings provide a platform to discuss current trends and hot topics, such as `Git` 😈 and `Python` 🐍**

# Join us! {background-image="images/background-joinus.png" background-size="800px" background-position="right"}

If you’d like to join our team and contribute to our community, we have a few open positions!

<br>

Fill out the form here 👇 <https://forms.gle/SkBiab8LhLcehpKu6>

## R-Ladies Rome in Numbers {background-image="https://i.giphy.com/media/v1.Y2lkPTc5MGI3NjExMnp5YmxpZTFoYWd2bDFpbHVnMDVhcDhkcmtrbmo2eXlrdXlhYXJhaiZlcD12MV9pbnRlcm5hbF9naWZfYnlfaWQmY3Q9Zw/TrOMR6REnWN1u/giphy.gif" background-opacity="0.5"}

::: {.callout .callout-info}
For more information, please visit [rladiesrome.org](rladiesrome.org)
:::

**`R-Ladies Rome`** has grown into a **`widely recognized community`**.

Since January 2023, we’ve welcomed over **`1.2K members`** on Meetup, gained **`2K+ RSVPs`**, and successfully organized **`25+ events`**.

```{r}
#| echo: false
#| message: false
#| warning: false
#| eval: false
library(meetupr)
rladies_rome <- get_events("rladies-rome")
rladies_rome_members <- meetupr::get_members("rladies-rome")
saveRDS(rladies_rome, "data/rladies_rome.rds")
saveRDS(rladies_rome_members, "data/rladies_rome_members.rds")
```

```{r}
#| echo: false
#| message: false
#| warning: false
library(tidyverse)
rladies_rome <- readRDS("data/rladies_rome.rds")
rladies_rome_members <- readRDS("data/rladies_rome_members.rds")
```

```{r}
events_rsvp <- rladies_rome %>%
  select(id,time,going)%>%
  mutate(time = as.Date(time,origin="1970-01-01"),
         time_id=row_number(time)) %>%
  arrange(time_id)%>%
  group_by(time_id,time) %>%
  reframe(going = sum(going))%>%
  mutate(tot_going = cumsum(going))


tot_members <- rladies_rome_members%>%
  mutate(created = as.Date(created,origin="1970-01-01"))%>%
  group_by(created)%>%
  reframe(members=n())%>%
  mutate(tot=cumsum(members))
```

```{r}
#| layout-ncol: 2
#| echo: false
events_rsvp%>%
  ggplot(aes(x = time, y = tot_going)) +
  geom_line() +
  geom_smooth(color = "purple", se = F)+
  scale_x_date(date_labels = "%b-%y",date_breaks="3 months") +
  labs(title = "R-Ladies Rome Events RSVP",
       subtitle = "Cumulative number of reservations",
       x = "Time(month-year)",
       y = "Number of Attendees",
  caption = "DataSource: {meetupr} R-package | Graphics: Federica Gazzelloni") +
  theme_minimal()+
    theme(plot.title = element_text(size=18,face="bold",hjust=0.5),
        plot.subtitle = element_text(size=14,face="bold",hjust=0.5),
        plot.caption = element_text(size=10,face="italic"))

  
tot_members%>%
  ggplot(aes(x = created,y=tot)) +
  geom_line() +
  geom_smooth(color = "purple", se = F)+
  scale_x_date(date_labels = "%b-%y",date_breaks="3 months") +
  labs(title = "R-Ladies Rome Membership Registration Growth",
       subtitle = "Cumulative number of members",
       x = "Time(month-year)",
       y = "Number of Members",
       caption = "DataSource: {meetupr} R-package | Graphics: Federica Gazzelloni") +
  theme_minimal() +
  theme(plot.title = element_text(size=18,face="bold",hjust=0.5),
        plot.subtitle = element_text(size=14,face="bold",hjust=0.5),
        plot.caption = element_text(size=10,face="italic"))
```
